---
title: "Homework 1"
author: "Adam Grottoli"
date: "January 13, 2020"
output: html_document
---

```{r setup, include=FALSE}
setwd("~/R/R practice/BioStats")
```

#PART I
##Question 1.
```{r} 
tsa=c(0.17,0.20,0.13,0.20,0.24,0.25,0.15,0.21,0.21)
tsb=c(0.47,0.21,0.34,0.32,0.33,0.29,0.18,0.20,0.25)
cs=c(0.44,0.33,0.37,0.33,0.31,0.27,0.22,0.30,0.28)
```


##Question 2.
```{r}
(mean(tsa)-mean(tsb))
```


##Question 3.
```{r}
(mean(tsa)-mean(cs))
```


##Question 4.
```{r}
hist(cs, xlab=expression(paste("Hydrogen peroxide (",mu,"moles/g)")), main = NULL)
```
Figure 1. Occurance of hydrogen peroxide concentrations in the leaves of common potatoes

##Question 5.
```{r message=FALSE, warning=FALSE}
hpo=c(0.27,0.21,0.34,0.32,0.24,0.29,0.18,0.20,0.29)
fgs_growth=c(1.79,1.01,1.71,1.89,1.41,1.15,1.13,1.20,1.10)
fgs_dfns=data.frame('Peroxide'=hpo,'Growth.rate'=fgs_growth)
library(knitr)
names(fgs_dfns)[2]=paste("Growth Rate")
kable(fgs_dfns, caption="Table 1. Fungus growth and hydrogen peroxide concentration in potato plant leaves")
```


##Question 6.
```{r}
plot(fgs_dfns, xlab=expression(paste('Hydrogen peroxide concentration (',mu,'moles/g)')), ylab='Fungal growth rate (cm/day)')
```
Figure 2. Fungal defense in leaves of potato plants in relation to hydrogen peroxide concentration

##Question 7.
The plot shows a positive trend with fungal growth increasing as hydrogen peroxide concentration increases. This trend disagrees with the hypothesis that hydrogen peroxide defends against fungal growth.

#PART II
##Question 8.
```{r}
turtle.success=read.csv("turtlenesting.csv")
```


##Question 9.
```{r message=FALSE, warning=FALSE}
library(knitr)
kable(table(turtle.success), caption = "Table 2. Outcomes of nesting attempts by 3 marine turtle species")
```

##Question 10.
```{r}
library(ggplot2)
ggplot(data=turtle.success, aes (x=Species, fill=Nesting.status)) +   geom_bar(position=position_dodge()) +
 labs(y='Number of Attempts',fill='Nesting Outcome') +
 ylim(0,20)
```
Figure 3. Number of successful and aborted nesting attempts in 3 species of marine turtle 

##Question 11.
```{r message=FALSE, warning=FALSE}
library(dplyr)
turtle_comb=data.frame(table(turtle.success))
turtle_comb %>% 
  group_by(Nesting.status) %>%
summarise(mean=mean(Freq))
turtle_comb %>% 
  group_by(Nesting.status) %>%
summarise(sd=sd(Freq))
```


##Question 12.
```{r}
turtle_comb %>% 
group_by(Species) %>%
summarise(Freq = Freq[Nesting.status == "Aborted"] / Freq[Nesting.status == "Success"])
```
Given that 75% of Hawksbill nesting attempts were aborted, I would choose this species as requiring the greatest conservation effort.

##Question 13. 
```{r}
turtle.eggs=read.csv("meaneggs.csv")
kable(turtle.eggs, caption = "Table 3. Average number of eggs layed by per nest at 16 beach sections in 3 marine turtle species")
```


##Question 14.
```{r}
ggplot(stack(turtle.eggs), aes (x=ind, y = values)) +
  geom_boxplot() +
  labs(y='Mean number of Eggs', x='Species') +
  ylim(80,160)
```
Figure 4. Average marine turtle eggs per nest at 16 beach sections

##Question 15.
```{r}
ggplot(data = turtle.eggs, aes(y = Leatherback, x = Hawksbill)) +
geom_point(size=2) +
ylim(80,150)
```
Figure 5. Average Leatherback vs Hawksbill turtle eggs per nest at 16 beach sections

